Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-22 Moltres.tex
spaces before citations

More recently, Aufiero et al. \cite{aufiero_development_2014} have begun to
approach transient simulations in the \gls{MSFR} within the finite volume
OpenFOAM multiphysics toolkit\cite{weller_tensorial_1998}.  This approach
benefits from pre-implemented turbulence models available in the OpenFOAM
library and captures the full-core three-dimensional geometry of the reactor
primary circuit.  OpenFOAM \gls{CFD} has additionally been shown by Laureau et
al. \cite{laureau_transient_2017} to couple well with Transient Fission Matrix
neutronics within the \gls{MSFR}.

@@

Moltres is an open source code licensed under \gls{LGPL} terms so the 
\gls{MSR} community can freely use, interrogate, and improve it.  Its openness 
is a defining characteristic and promotes
quality through transparency and ease of peer review. In the era of
GitHub\cite{github_build_2017} and international scientific collaboration,
open and modern software practices must be employed in order for nuclear
engineering simulation capability to enable discovery and support the regulatory
needs presented by new reactor designs. In that vein, Moltres uses
\mintinline{latex}{git} for version control, integration testing to protect
developed physics capabilities, and a C++ object-oriented design to
enable extension and code reuse. While export control laws have the potential 
to restrict openness of neutron transport software that is dual use, there is 
no reason to believe that Moltres could be used for weapons proliferation. 
Moltres requires that cross sections be provided by the user, implements a 
combination of algorithms that can be easily derived from open literature, is 
tailored to molten salt reactor physics. Accordingly, Moltres joins a veritable 
parade of open academic nuclear engineering software such as 
OpenMC\cite{romano_openmc:_2015}, OpenMOC\cite{boyd_openmoc_2014}, and 
PyNE\cite{bates_pyne_2014,biondo_quality_2014}.

>>>>

More recently, Aufiero et al. \cite{aufiero_development_2014} have begun to
approach transient simulations in the \gls{MSFR} within the finite volume
OpenFOAM multiphysics toolkit \cite{weller_tensorial_1998}.  This approach
benefits from pre-implemented turbulence models available in the OpenFOAM
library and captures the full-core three-dimensional geometry of the reactor
primary circuit.  OpenFOAM \gls{CFD} has additionally been shown by Laureau et
al. \cite{laureau_transient_2017} to couple well with Transient Fission Matrix
neutronics within the \gls{MSFR}.

@@

Moltres is an open source code licensed under \gls{LGPL} terms so the 
\gls{MSR} community can freely use, interrogate, and improve it.  Its openness 
is a defining characteristic and promotes
quality through transparency and ease of peer review. In the era of
GitHub \cite{github_build_2017} and international scientific collaboration,
open and modern software practices must be employed in order for nuclear
engineering simulation capability to enable discovery and support the regulatory
needs presented by new reactor designs. In that vein, Moltres uses
\mintinline{latex}{git} for version control, integration testing to protect
developed physics capabilities, and a C++ object-oriented design to
enable extension and code reuse. While export control laws have the potential 
to restrict openness of neutron transport software that is dual use, there is 
no reason to believe that Moltres could be used for weapons proliferation. 
Moltres requires that cross sections be provided by the user, implements a 
combination of algorithms that can be easily derived from open literature, is 
tailored to molten salt reactor physics. Accordingly, Moltres joins a veritable 
parade of open academic nuclear engineering software such as 
OpenMC \cite{romano_openmc:_2015}, OpenMOC \cite{boyd_openmoc_2014}, and 
PyNE \cite{bates_pyne_2014,biondo_quality_2014}.
